---
title: "VIS2128A1"
author: "Daniel Montoya"
date: "9/6/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading Packages

Installation of essential packages necessary for the visualization and manipulation of Washington D.C.'s data.

```{r load packages, message=FALSE}
library(sf)
library(tidyverse)
library(ggthemes)
library(ggspatial)
```

## Loading Datasets

Installation of three data sets based in Washington D.C. The three data sets represent:
  1. *Urban Tree Canopy by Landuse* examining green spaces in Washington D.C.
  2. *Bike Trails* focusing on park areas and paths along the National Mall.
  3. *Potential Landmarks* representing historically significant structures.

```{r load datasets}
Landmarks <- st_read("Potential_Landmarks.geojson", quiet = TRUE)

Trails <- st_read("Bike_Trails.geojson", quiet = TRUE)

Canopy <- st_read("Urban_Tree_Canopy_by_2015_Landuse.geojson", quiet = TRUE)
```

## Basic Plot Lines

```{r}
Landmarks_plot <- ggplot(Landmarks) +
  geom_sf(size = 0.35)
Trails_plot <- ggplot(Trails) +
  geom_sf()

Landmarks_plot
Trails_plot
```
## Aesthetics

```{r}

  ggplot() +
  geom_sf(data = Canopy, color = NA, size = 0.01,
          aes(fill = "Tree Canopy")) +
  geom_sf(data = Landmarks, color = "black", 
          aes(fill = "Potential Landmarks")) +
  geom_sf(data = Trails) +
  scale_fill_manual(values = c("red4", "green4"), name = "") +
  theme_map() +
  ggtitle("Bike Routes around Washington D.C.")

```
## Open Source Maps

```{r, results='hide'}
ggplot(Trails) +
  annotation_map_tile (zoomin = 0, progress = "none") +
    geom_sf() +
    labs(caption = "Map tiles and data by OpenStreetMap")
```
## Gotham City by Bike

```{r, results='hide'}
ggplot() +
  annotation_map_tile(zoomin = 10, progress = "none", type = "cartodark") +
    geom_sf(data = Trails, color = "yellow") +
    geom_sf(data = Landmarks, fill = "yellow", color = "yellow") +
    labs(caption = "Map tiles and data by OpenStreetMap") 
 
```
## Celebrating Vexillology

This map utilizes the polygons in questions and transforms them into a symbolic representation of the flag of Washington D.C. The origin and design can be viewed in this link: https://usflags.design/washington-dc/

```{r}
ggplot() +
  geom_sf(data = Canopy, color = NA, size = 0.01,
          aes(fill = "Tree Canopy")) +
  geom_sf(data = Landmarks, color = "gray", 
          aes(fill = "Bike Routes to Potential Landmarks")) +
  geom_sf(data = Trails, color = "red2") +
  scale_fill_manual(values = c("red2", "white"), name = "")

```

